### 2015-12-26 docs/ms_communitySynchrony.Rmd
updates figures with poly vs mono

## rmarkdown render options
output:
  pdf_document:
    fig_caption: true
    keep_tex: false
fontsize: 12pt
geometry: margin=1in

---
```{r caching, include=FALSE}
library("methods")
library("knitr")
basename <- "ms_communitySynchrony"
opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
               cache.path = paste("components/cache/", basename, "/", sep=""))
opts_chunk$set(cache = 2)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
               comment = NA, verbose = TRUE, echo=FALSE)

@@

\begin{figure}[!ht]
  \centering
      \includegraphics{./components/envresp_vs_ipmsynch.png}
  \caption{Average synchrony of IPM-simulated per capita growth rates (from 13 year sections) as a function of the average synchrony of the vital rate random year effects for each site. Community sychrony is expected to approximately equal the synchrony of species' environmental responses in the absence of demographic stochasticity and strong interspecific interactions. The synchrony of species' random year effects across vital rates is a strong ($\text{R}^2$ = 0.67), but not perfect, predictor of community synchrony. Points are labeled by site codes: AZ = Arizona, ID = Idaho, KS = Kansas, MT = Montana, and NM = New Mexico.}
\end{figure}

>>>>

## rmarkdown render options
output:
  pdf_document:
    fig_caption: true
    keep_tex: false
fontsize: 12pt
geometry: margin=1in
linkcolor: black
urlcolor: black
---
```{r caching, include=FALSE}
library("methods")
library("knitr")
basename <- "ms_communitySynchrony"
opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
               cache.path = paste("components/cache/", basename, "/", sep=""))
opts_chunk$set(cache = 2)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
               comment = NA, verbose = TRUE, echo=FALSE)

@@

<!--
\pagebreak{}

\begin{figure}[!ht]
  \centering
      \includegraphics{./components/envresp_vs_ipmsynch.png}
  \caption{Average synchrony of IPM-simulated per capita growth rates (from 13 year sections) as a function of the average synchrony of the vital rate random year effects for each site. Community sychrony is expected to approximately equal the synchrony of species' environmental responses in the absence of demographic stochasticity and strong interspecific interactions. The synchrony of species' random year effects across vital rates is a strong ($\text{R}^2$ = 0.67), but not perfect, predictor of community synchrony. Points are labeled by site codes: AZ = Arizona, ID = Idaho, KS = Kansas, MT = Montana, and NM = New Mexico.}
\end{figure}
-->
\pagebreak{}

\begin{figure}[!ht]
  \centering
      \includegraphics{./components/poly_vs_mono_synch.png}
  \caption{Synchrony of communities simulated without interspecific interactions (monoculture) versus synchrony of communities simulated with interspecific interactions (polyculture). We used the same sequence of random year effects for both simulations (mono and polyculture) to mimic biodiversity-ecosystem function experiments. The dashed line is the line of equality.}
\end{figure}
